Adapting the Chumbley Score to Bullet Striations

### 2018-04-25 presentation/presentation.Rmd
presentation +s

## Conclusions Failed Tests

- The number of failed tests is highly dependent on the size of the comparison windows and is correlated to the ground truth, 
- Higher for known same-sourced lands than for known different sourced lands. 
- The \textbf{CS1} algorithm fails to conduct a test about 8 to 13 % of the time for known same-source lands, and 2 to 6% of the time for known different source lands.
- number of failed tests for CS1 is always higher than the corresponding theoretical number of failed tests.
- Using CS2, the case with \textbf{largest} # of failed tests is still \textbf{lower} than the case where CS1 gives the \textbf{lowest} # of failed tests
- Even when the coarseness is high, CS2 will have lower number of failed tests than CS1, Making it more robust.
- CS2 performs better for both same and different-sources
- Solves a critical issue of CS1 known same-source matching, by having a negligible number of Known same-source failed tests

@@

#### CS1
- Best works for $w_o$ of $\approx$ 130 to 160 and $w_v$ 50 when the smoothing is $c$ $\approx$ 0.3.
- The Type II rate is lowest for a nominal $\alpha$ of 5%, with type I error rate of  6.2% and the Type II error rate of 24%. 
- For lower nominal alpha levels of 1%, 0.5% and 0.1% the lowest type II error rate increases to about 36.4%, 41% and 52.5% respectively.
- Gets worse for coarseness 0.15

#### CS2
- For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. 
- Smaller validation sizes $w_v$ are typically associated with a smaller type II error.
- CS2 shows an increase in the power of the test.
- Fix in CS2 will also improve power for matching toolmarks.
- While significantly reduced over CS1, CS2 still has type 2 error rates on bullet lands that are  higher than the error rates achieved on the -much larger- toolmarks.
- Might be able to get more power out of the test by adapting C2 in a bullet-to-bullet comparison.

>>>>

## Conclusions Failed Tests
\fontsize{10pt}{11}\selectfont

- Number is highly dependent on the comparison window sizes
- Correlated to the ground truth, 
- \textbf{Higher for known same-sourced lands (CS1)} than for known different sourced lands. 
- \textbf{CS1} fails to conduct a test about 8 to 13 % of the time for \textbf{known same-source lands}, and 2 to 6% of the time for \textbf{known different source lands}.
- Number for CS1 always higher than the corresponding theoretical number of failed tests.
- Using CS2, the case with \textbf{largest} # of failed tests is still \textbf{lower} than the case where CS1 gives the \textbf{lowest} # of failed tests
- Even for high coarseness, CS2 will have lower number of failed tests than CS1, Making it more robust.
- CS2 performs better for \textbf{both} same and different-sources
- Solves a \textbf{critical issue} of CS1 known same-source matching, by having a \textbf{negligible number of Known same-source failed tests}

@@

#### CS1
- Best works best for $w_o$ of $\approx$ 130 to 160 and $w_v$ 50 when the smoothing is $c$ $\approx$ 0.3.
- The Type II rate is lowest for a nominal $\alpha$ of 5%, with type I error rate of  6.2% and the Type II error rate of 24%. 
- For lower nominal alpha levels of 1%, 0.5% and 0.1% the lowest type II error rate increases to about 36.4%, 41% and 52.5% respectively.
- Gets worse for coarseness 0.15

#### CS2
- Significantly reduced over CS1
- For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. - Smaller validation sizes $w_v$ are typically associated with a smaller type II error.
- CS2 shows an increase in the power of the test.
- Type II CS2, still much higher for bullet lands than for toolmarks.
- Fix in CS2 will also improve power for matching toolmarks thans CS1
- Bullet-to-bullet comparison using CS2 $\approx$ more power out of the test.

## ROC Curves
\fontsize{10pt}{11}\selectfont
\begin{figure}[hbtp]
\centering
\includegraphics[width=0.9\textwidth]{imgs/roc-curves.png}
\caption{\label{roc-curves}  ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$.}
\end{figure}

\vspace{-0.5em}

- Superior performance of CS2 over CS1
- Best performances wrt  ROC curves are reached for $w_0$ 150 and higher. 
- Points of equal error rates (EERs): intersection of the dotted line and the ROC curves.

### \textbf{THANK YOU. Questions?}
